Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-15 paper/sec-results.tex
updating permille label, increasing figure sizes

SC

For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
- compute data/prediction plots\\
- compute chi2\\

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}
    \caption{PineAPPL comparison for ATLAS high-mass Drell-Yan.}
    \label{fig:atlaszhighmass49fb}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin1}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin2}
    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin3}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin4}
    \includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin5}\includegraphics[width=0.4\textwidth]{figures/pineappl_CMSDY2D11_bin6}
    \caption{PineAPPL comparison for CMS 2D Drell-Yan.}
    \label{fig:cmsdy2d11}
\end{figure}
